Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-11-16 main.tex
Small structure changes, deleted appendix (close #9)

@@

\subsection{Automatic Changes of Inputs in Maple}\label{subsec:maple-probs}
\Maple{} evaluates inputs automatically and changes the input into an internal representation. This internal representation might look a bit different to the input. One example has already been given with \Cref{fig:internal-maple-dag}, where each summand of a sum is stored with a factor. Here is a list of all internal changes that occur for inputs.

@@

\emergencystretch=1em
\printbibliography
\end{document}

>>>>

Miller also developed LaTeXML, a tool for converting \LaTeX{} expressions to MathML~\parencite{LaTeXML}. LaTeXML was used to generate the \gls*{dlmf} and is able to parse the \Macro s to content MathML. Even though many \gls*{cas} are able to import and export MathML, they fail for special functions. Schubotz et.~al recently performs benchmarks on several \LaTeX{} to MathML conversion tools, including LaTeXML, in~\parencite{DBLP:conf/jcdl/SchubotzGSMCG18}.

@@

\subsection{Automatic Changes of Inputs in Maple}\label{subsec:maple-probs}
In this section, we will discuss several techniques to get access to the parse tree of \Maple's input. The translation process from this parse tree than follows the same principle as for the forward translations.

\Maple{} evaluates inputs automatically and changes the input into an internal representation. This internal representation might look a bit different to the input. One example has already been given with \Cref{fig:internal-maple-dag}, where each summand of a sum is stored with a factor. Here is a list of all internal changes that occur for inputs.

@@

\emergencystretch=1em
\printbibliography

%\appendix
%\section*{Appendix}
\end{document}
